### 2021-10-21 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
more minor formatting changes

\end{paracol}
\begin{figure}[h]
    \widefigure
    \includegraphics[width=10 cm]{Definitions/counter-flow-hx.pdf}
    \caption{Simplified counter-flow heat exchanger diagram. \label{counter-flow-hx}}
\end{figure}
\begin{paracol}{2}
\linenumbers
\switchcolumn

@@

\begin{specialtable}[H]  
    %[htbp]
    \caption{Calculated system parameters for charging cycle configurations with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-charg}}
    \resizebox{\columnwidth}{!}{
        \begin{tabular}{lc|c|cc|ccc}
            \toprule
            &  & \textbf{C-LFR-PRE} & \multicolumn{2}{c|}{\textbf{C-LFR-PAR}}  &	\multicolumn{3}{c}{\textbf{C-LFR-CIRC}} \\
            \textbf{Definition} & \textbf{Variable} & \textit{C} & \textit{C} & \textit{C} & \textit{C} &	\textit{C}	&	\textit{C}\\
            \midrule
            Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	390	&	440	&	390	&	410	&	440	\\
            LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4,1C}$	&	400	&	400	&	400	&	400	&	400	&	400	\\
            Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	34.53	&	45.30	&	45.30	&	99.92	&	89.66	&	74.29	\\
            Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	&	0	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	&	519.6	&	519.6	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	&	118.9	&	118.9	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	&	77.28	&	77.28	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	&	196.2	&	196.2	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	0.7245	&	98.25	&	244.2	\\
            MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	&	0.7844	&	0.7844	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            C2S Mass Flow Fraction (-)	&	$y_{2}$	&	$\cdot$	&	0.6867	&	0.6867	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	6.99	&	22.83	&	22.83	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	&	0.8473	&	0.8743	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	&	366.4	&	366.4	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	&	0.8742	&	0.8742	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	41.69	&	42.69	&	42.69	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	&	0.8143	&	0.8143	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	&	1160	&	1160	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	&	0.9627	&	0.9627	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            C2S UA Value (MW/$^{\circ}$C)	&	$UA_{C2S}$	&	9.04	&	8.037	&	14.24	&	48.29	&	43.16	&	35.63	\\
            C2S Capacitance Ratio (-)	&	$CR_{C2S}$	&	0.4735	&	0.7556	&	0.9339	&	0.8755	&	0.8599	&	0.8294	\\
            C2S Heat Transfer Rate (MW)	&	$\dot{Q}_{C2S}$	&	328	&	430.4	&	430.4	&	949.3	&	851.8	&	705.8	\\
            C2S Effectiveness (-)	&	$\varepsilon_{C2S}$	&	0.9368	&	0.8275	&	0.8307	&	0.9511	&	0.9459	&	0.9355	\\
            C2S Approach Temperature ($^{\circ}$C)	&	$\delta_{C2S}$	&	10	&	35	&	26.27	&	10	&	10	&	10	\\
            \bottomrule
        \end{tabular}
        }
    \end{specialtable}
    % \begin{paracol}{2}
        % \linenumbers
        % \switchcolumn

>>>>

% \end{paracol}
\begin{figure}[h]
    \widefigure
    \includegraphics[width=10 cm]{Definitions/counter-flow-hx.pdf}
    \caption{Simplified counter-flow heat exchanger diagram. \label{counter-flow-hx}}
\end{figure}
% \begin{paracol}{2}
% \linenumbers
% \switchcolumn

@@

\begin{specialtable}[H]  
    %[htbp]
    \caption{Calculated system parameters for charging cycle configurations. All cases were evaluated with constrained (\textit{C}) lead-cooled fast reactor low-end temperature.\label{tab-charg}}
    \resizebox{\columnwidth}{!}{
        \begin{tabular}{lc|c|cc|ccc}
            \toprule
            &  & \textbf{C-LFR-PRE} & \multicolumn{2}{c|}{\textbf{C-LFR-PAR}}  &	\multicolumn{3}{c}{\textbf{C-LFR-CIRC}} \\
            \textbf{Definition} & \textbf{Variable} & \textit{C} & \textit{C} & \textit{C} & \textit{C} &	\textit{C}	&	\textit{C}\\
            \midrule
            Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	390	&	440	&	390	&	410	&	440	\\
            LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4,1C}$	&	400	&	400	&	400	&	400	&	400	&	400	\\
            Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	34.53	&	45.30	&	45.30	&	99.92	&	89.66	&	74.29	\\
            Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	&	0	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	&	519.6	&	519.6	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	&	118.9	&	118.9	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	&	77.28	&	77.28	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	&	196.2	&	196.2	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	0.7245	&	98.25	&	244.2	\\
            MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	&	0.7844	&	0.7844	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            C2S Mass Flow Fraction (-)	&	$y_{2}$	&	$\cdot$	&	0.6867	&	0.6867	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	6.99	&	22.83	&	22.83	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	&	0.8473	&	0.8743	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	&	366.4	&	366.4	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	&	0.8742	&	0.8742	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	41.69	&	42.69	&	42.69	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	&	0.8143	&	0.8143	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	&	1160	&	1160	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	&	0.9627	&	0.9627	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
            C2S UA Value (MW/$^{\circ}$C)	&	$UA_{C2S}$	&	9.04	&	8.037	&	14.24	&	48.29	&	43.16	&	35.63	\\
            C2S Capacitance Ratio (-)	&	$CR_{C2S}$	&	0.4735	&	0.7556	&	0.9339	&	0.8755	&	0.8599	&	0.8294	\\
            C2S Heat Transfer Rate (MW)	&	$\dot{Q}_{C2S}$	&	328	&	430.4	&	430.4	&	949.3	&	851.8	&	705.8	\\
            C2S Effectiveness (-)	&	$\varepsilon_{C2S}$	&	0.9368	&	0.8275	&	0.8307	&	0.9511	&	0.9459	&	0.9355	\\
            C2S Approach Temperature ($^{\circ}$C)	&	$\delta_{C2S}$	&	10	&	35	&	26.27	&	10	&	10	&	10	\\
            \bottomrule
        \end{tabular}
        }
    \end{specialtable}
    % \begin{paracol}{2}
        % \linenumbers
        % \switchcolumn
